---
title: "Student Sit In"
author: "Moises Sales"
date: "10/28/2019"
output: 
  html_document:
    toc: true
    number_sectons: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# ONE SHOT assignment!
this is an extra credit assignment, must be completed Monday Oct 28, turn-in closes at midnight!

## Problem statement: 
Students at UCD- is there a relation between where one sits and one's major? 

## Introduction  

<!-- where is the data found?  Is this an experiment or an observational study?  !-->

Data from this study came from... 



```{r include=FALSE, echo=FALSE}
library(tigerstats)
data(ucdavis1)

```

$H_0$: there is no relationship between one's major and where one sits in a class   
$H_A$: where one sits in class and one's major are related  

<!-- Get the data: !-->

names of the data in the data frame

```{r echo=FALSE}
UCDdataframe = data.frame(seat=ucdavis1$Seat, major=ucdavis1$class, data=ucdavis1)
names(UCDdataframe)
```
## Methods

<!--  describe analysis methods here 
what are the variable types, and indicate gaphical, numerical, and inferential methods appropriate
for this question  !--> 

Both Variables in this analysis are categorical, hence we use bar graphs and tables to summarize the data and a chi square test for inference.

## Data summary

**Graphical summary**
put the graphic description of the data here

```{r}
barchartGC(~seat+major, data = UCDdataframe, type = "percent", xlab = "Seating", main = "Seating vs Major")
```

This bar chart shows us that most Liberal Arts majors prefer to sit towards the front of the class while most NonLiberal Arts majors prefer to sit towards the back. Although it seems like as if the middle seating for both Liberal Art majors and NonLiberal Art majors is favored around the same amount from there main seating preference which would be front seating for Liberal arts and Back seating for NonLiberal arts.

**Numerical summary**
put numerical summary here

```{r}
tab1 = xtabs(~seat+major, data = UCDdataframe)
    rowPerc(tab1)
```

The numerical results show that Liberal Art students have around a 21% favoring to seating in the front while showing a 13% to favoring seating in the middle. There is roughly a small 8% difference in seating between these two while NonLiberal arts students show a similar low percentage of a difference of ~5% between the Back favored seating of 91% to the Middle 86% seating.

## Inferential Results
put the inferential test for the the null hypothesis here

```{r}
chisqtestGC(tab1) 
```

The p-value is 0.2173 which means that we fail to reject the null hypothesis.

## Results and conclusions

<!-- explain-- is there evidence that certain majors tend to sit in particular areas of the class?  Can the results of this test be generalized to all majors in all universities? !-->

From our p-value result of 0.2173 we fail to reject the null hypothesis "$H_0$: there is no relationship between one's major and where one sits in a class". This is further supported when looking at data from our bar graph as the middle seating in the class is favored for both Liberal arts and NonLiberal arts majors showing no difference in seating for majors. In our numerical results there is a less than a 10% difference amongst the main favored seatings and the middle sections of seating for Liberal Art majors and NonLiberal Art majors showing that there is a low difference to what can be determined as a favored seating from either the front, middle, or back. The overall survey looks at roughly around 173 students for the data at UCD which is a low amount of students for a university for a survey. Due to this we can determine that this test can not be used to generalize all majors in all universities.


<!--
push results to your github account, turn in the URL

--OR--

If you did not fork my repo to your github account,
create a repository in your github account for this project, get the URL for that repo and 
(in the terminal window..)

$git remote add origin URL_of_your_github_repo
$git push -u origin master

!-->